Democratizing Secure Two-Party Computation

### 2017-10-12 OaklandSubmission/ex.tex
edits and comments to Sec 1 and 2.

A potential customer Alice might not want to reveal $x$ to Bob because of privacy concerns.
And Bob does not want to reveal $w$ and $b$ because then Alice can steal the model.
SMC can help Alice and Bob compute $w^Tx>b$ securely, such that Alice receives the classifier's
prediction and Bob learns nothing about $x$. Moreover, Alice does not learn anything more about $w$
and $b$ than what is revealed by the prediction.

To implement this system, Bob can write the code in \tool and this code is shown in Figure~\ref{fig:ex-sml}.
The expression {\tt input1} reads a value from Bob and {\tt input2} reads from Alice.
The language has arrays and simple loops. A loop {\tt for i = [0:N]} repeats its
body {\tt N} times, the loop counter {\tt i} is assigned {\tt 0} in the first iteration,
and is incremented by one after each iteration. Unbounded {\tt while} loops are problematic
from a cryptographic standpoint and our language only permits these simple {\tt for} loops. 
The first loop in Figure~\ref{fig:ex-sml} reads the model $w$ from Bob, the second loop reads
Alice's medical report $x$, and the third loop computes the dot product $w^Tx$.
The last {\tt output} statement sends the result of the comparison $w^Tx>b$ to Alice.
In particular, the ternary ``{\tt ? :}" operator performs a branch and the result is the second (third)
argument if the first argument is true (false).

@@

Moreover, it is difficult to maintain the code in Figure~\ref{fig:ex-aby}.
For example, if the multiplication is changed to a bitwise-or then,
in the absence of \tool, an efficiency-conscious developer would need to  use boolean circuits everywhere and would be tasked with removing all arithmetic circuits and the interconversion gates. 
 With \tool, the developer needs to change only a single character (replace {\tt *} in Figure~\ref{fig:ex-sml} with {\tt |}) to achieve the same effect. 
On this example and other small examples, we have found that the compiler generated C++ code from a \tool implementation is as efficient as manually written C++ code. In particular, for $w^Tx>b$, the compiler automatically generates code that uses arithmetic circuits for dot product and inserts appropriate conversion gates. Finally, although this paper uses ABY for evaluation, the  compiler can be easily retargeted to generate code for other cryptography backends.

The \tool compiler provides strong static guarantees. For example, a well typed
\tool program is guaranteed to execute to termination without errors. A \tool program cannot go into non-termination or dereference illegal memory, i.e., no buffer overflows or underflows can happen at run time. This guarantees are
much stronger than what are offered by production compilers such as {\tt gcc}.
The primary reason that we are able to achieve these guarantees is because
\tool has been designed to be verifiable and is backed by formal semantics. 
Furthermore, the compiler output is guaranteed to be a cryptographically secure
implementation of the functionality declared by the \tool code. 
Moreover, the \tool compiler also generates a C implementation that can be run natively on a single machine for functional testing.

>>>>

A potential customer Alice might not want to reveal $x$ to Bob because of privacy concerns.
And Bob does not want to reveal $w$ and $b$ because then Alice can steal the model.
SMC can help Alice and Bob compute $w^Tx>b$ securely, such that Alice receives the classifier's
prediction and Bob learns nothing about $x$. Moreover, Alice does not learn anything more about $w$
and $b$ than what is revealed by the prediction. 
\nc{This is a bit repetitive from the intro, isnt it? Should we have another example perhaps?}
To implement this system, Bob can write the code in \tool and this code is shown in Figure~\ref{fig:ex-sml}.
The expression {\tt input1} reads a value from Bob and {\tt input2} reads from Alice.
The language has arrays and simple loops. A loop {\tt for i = [0:N]} repeats its
body {\tt N} times, the loop counter {\tt i} is assigned {\tt 0} in the first iteration,
and is incremented by one after each iteration. Unbounded {\tt while} loops are problematic
from a cryptographic standpoint and our language only permits these simple {\tt for} loops. 
The first loop in Figure~\ref{fig:ex-sml} reads the model $w$ from Bob, the second loop reads
Alice's medical report $x$, and the third loop computes the dot product $w^Tx$.
The last {\tt output} statement sends the result of the comparison $w^Tx>b$ to Alice.
In particular, the ternary ``{\tt ? :}" operator performs a branch and the result is the second (third)
argument if the first argument is true (false).

@@

Moreover, it is difficult to maintain the code in Figure~\ref{fig:ex-aby}.
For example, if the multiplication is changed to a bitwise-or then,
in the absence of \tool, an efficiency-conscious developer would need to  use boolean circuits everywhere and would be tasked with removing all arithmetic circuits and the interconversion gates. 
 With \tool, the developer needs to change only a single character (replace {\tt *} in Figure~\ref{fig:ex-sml} with {\tt |}) to achieve the same effect. 
On this example and other small examples, we have found that the compiler generated C++ code from a \tool implementation is as efficient as manually written C++ code. In particular, for $w^Tx>b$, the compiler automatically generates code that uses arithmetic circuits for dot product and inserts appropriate conversion gates. Finally, although this paper uses ABY for evaluation, the  compiler can be easily retargeted to generate code for other cryptography backends.
\nc{I like the above point. Perhaps we can mention something like this earlier in the intro itself?}
The \tool compiler provides strong static guarantees. For example, a well typed
\tool program is guaranteed to execute to termination without errors. A \tool program cannot go into non-termination or dereference illegal memory, i.e., no buffer overflows or underflows can happen at run time. These guarantees are
much stronger than what are offered by production compilers such as {\tt gcc}.
The primary reason that we are able to achieve these guarantees is because
\tool has been designed to be verifiable and is backed by formal semantics. 
Furthermore, the compiler output is guaranteed to be a cryptographically secure
implementation of the functionality declared by the \tool code. 
Moreover, the \tool compiler also generates a C implementation that can be run natively on a single machine for functional testing.
